\subsection{Motivation and objective}
\label{section:motivation_objective}

Motivations and objectives of this master thesis are:

\begin{enumerate}
  \setcounter{enumi}{0}
  \item To assess the technologies for 3D video capture and representation, targeting video meetings.
\end{enumerate}

2D traditional RGB cameras have good performance and are widely used. At Logitech, they are used as webcams, for video surveillance, for video conferences and more recently for streamers. Connected conference rooms is a key market of the current Logitech market. However, the video stream of 2D cameras depends on where the camera is placed in the room, therefore, the point of view is fixed. This fixed point of view could be a problem if the different people in the room are not well placed in respect to the camera or if the room does not have an appropriate size. Indeed, the different people who are looking at the conference with their computer could feel excluded from the conversation. Changing the point of view is a solution to improve the immersion. For this purpose, RGB-D cameras are used in this thesis to render the scene in 3D. It enables the possibility to change the point of view freely. As Logitech has no previous experience with such a technology, this thesis investigate 3D video capture and representation in a meeting room scenario.

\begin{enumerate}
  \setcounter{enumi}{1}
  \item To propose a pipeline for capturing and representing 3D video content with multiple cameras.
\end{enumerate}

In this thesis, the different algorithms and solution are developed for two cameras. However, it can be generalised to more cameras. The challenges met with two cameras are relevant to the ones faced with more cameras. A pipeline is proposed for capturing, calibrating, processing and rendering 3D videos of point clouds. 

% \begin{enumerate}
%   \setcounter{enumi}{2}
%   \item  To propose an appropriate supply chain strategy for the launch phase of the product regarding the uncertainty of the demand during the ramp-up phase.
% \end{enumerate}
% The third issue faced is related to the market itself. \textit{LMB} is used to provide products to its sister companies. For the LH30VO, the sellers plan to sell half of the products to the internal market and the other half to the external market. 
% The situation about future sales and the demand during the ramp-up phase is uncertain. The objective is to provide solutions and guidance to prepare the company for the uncertain ramp-up.




